% work_experience.tex
\subsection*{\color{CarianBlue} \Large Work Experience \crulefill{1pt}}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
    \item \headerrow
        {\textbf{Engineering Manager | CPP Investments | Mumbai | Toronto | Dec 2021 - Present}}
        {Technology and Data, Public Markets}
        \begin{itemize*}
            \item Managed and empowered a diverse team of \textbf{10 highly skilled professionals}, overseeing the design and development of cutting-edge software products and spearheading digital transformation initiatives.
            \item Implemented Agile methodologies, resulting in a 20\% increase in project completion rate and reduced time-to-market by 15\%.
            \item Implemented SBL auto locate and PB Cross capability through Traiana integration, optimizing existing \textbf{\$20 billion CAD} of give-eligible swap balances, leading to \textbf{material cost savings of \$20 million} and over \textbf{860 hours saved annually} for the trading team.
            \item Revamped One Tick by re-platforming it on AWS cloud, resulting in an outstanding \textbf{70\% performance improvement}, along with \textbf{\$213,000} in hardware upgrade savings and a projected data savings of \textbf{\$707,800} over five years.
            \item Upgraded FIS Apex, saving \textbf{480 annualized hours} and enhancing efficiency in collateral management.
        \end{itemize*}

    \item \headerrow
        {\textbf{Senior Software Engineer III | Bank Of America | Mumbai | Sep 2017 - Dec 2021}}
        {Equity Linked Technology, Investable Indices}
        \begin{itemize*}
            \item Co-Led a \textbf{globally distributed team of 13 software developers} to successfully build and maintain an investable indices platform comprising \textbf{400 indices}. The platform scaled to accommodate a \textbf{13-fold increase} in calculations (strategy, lifecycle, reconciliation, publication, reporting) and a \textbf{3-fold increase} in market data REST requests over a span of four years.
            \item Analyzed market data cost drivers and achieved significant savings of \textbf{\$350 million} through optimization using caching and alternative sourcing.
        \end{itemize*}

    \item \headerrow
        {\textbf{Consultant | NRIFT | Mumbai | Jul 2015 - Aug 2017}}
        {Deutsche Bank, Financing Team}
        \begin{itemize*}
            \item Led a team of 4 software developers to develop a Python-based reporting framework in an Agile environment. The framework separates content generation, report formatting, and report delivery into reusable configurations and supports email (using Jinja), PDF, Excel, CSV, and delivery channels like mail and SFTP. This initiative resulted in an impressive \textbf{90\% reduction} in client reporting FTE efforts.
        \end{itemize*}

    \item \headerrow
        {\textbf{Consultant | Cognizant | Mumbai | Mar 2013 - Jul 2015}}
        {Credit Suisse, Global Market Risk Reporting}
        \begin{itemize*}
            \item Achieved a \textbf{20\% reduction} in SLA breaches caused by technical incidents in APAC/EMEA regulatory risk report generation through workflow optimization and re-modeling. Spearheaded design discussions, confluence, agile meetings, data modeling, requirement analysis, and maintenance for Market Risk Systems, leading to increased stability and process resilience.
        \end{itemize*}

    \item \headerrow
        {\textbf{Associate System Analyst | NSE Infotech | Mumbai | Dec 2009 - Mar 2013}}
        {Futures and Options Clearing and Settlement System}
        \begin{itemize*}
            \item Led a \textbf{team of 5 system analysts} in the end-to-end development of a robust derivative clearing and settlement system (listed futures and options). Conducted code reviews, optimized queries, mentored team members, and ensured error-free and timely delivery in high-pressure, regulator-driven environments. Additionally, spearheaded automation projects resulting in an aggregate \textbf{1.2 FTE} reduction and \textbf{\$50k+} yearly cost savings through \textbf{application decommissioning and workflow optimization}.
        \end{itemize*}
\end{itemize}
