\documentclass[letterpaper, 11pt]{article}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}

\geometry{left=0.75in, top=0.75in, right=0.75in, bottom=0.75in}

\definecolor{CarianBlue}{RGB}{28, 57, 187}

\newcommand{\crulefill}[2][0.4ex]{%
	\leavevmode\leaders\hrule height#1 depth \dimexpr#1-#2\hfill\kern0pt%
}

\begin{document}
% Header
{\LARGE \textbf{Pranav Gandhi}} \\
Technology Area Lead \\
Email: \href{mailto:pranavgandhi01@gmail.com}{pranavgandhi01@gmail.com} \ \ \textbar \ \  Phone: (91) 900-4949-611 \ \ \textbar \ \  LinkedIn: \href{https://linkedin.com/in/technologyenabler}{linkedin.com/in/technologyenabler}

% Professional Summary
\section*{\color{CarianBlue} \Large Professional Summary \crulefill{1pt}}
\begin{description}
    \item[$\bullet$ ] A results-driven leader with a strong focus on driving excellence and fostering collaborative environments for successful project delivery. Over \textbf{15+ years of diverse software engineering experience} with specialties in \textbf{software architecture, DevOps operation, backend development, and AWS cost optimization}. Led success in various product domains, including \textbf{FIS Quantum (Cash Management), FIS Apex (Collateral and Margin Management), OneTick (time-series database), Bloomberg \& Reuters API (Public Market Data), Investable Indices, and Traiana (PB Cross Swaps and SBL short optimization)}. 
    \item[$\bullet$] Love to contribute to open sources and tech communities by sharing knowledge and experience. Prefer a command line interface environment as a big fan of \textbf{OpenSource, Linux, ChatGpt, and Python}. Interested in devising a better problem-solving method for \textbf{challenging tasks}, and \textbf{learning new technologies and tools}. A \textbf{team player} in making better strategic decisions, solving problems, and contributing positively to a value-driven organization.
  \end{description}

% Work Experience
\section*{\color{CarianBlue} \Large Work Experience \crulefill{1pt}}
\begin{itemize}
    \item \textbf{Manager | CPP Investments | Mumbai | Toronto | Dec 2021 - Present} \\
    \textit{Technology and Data, Public Markets}
    \begin{itemize}[leftmargin=1em]
        \item Managed and empowered a diverse team of \textbf{10 highly skilled professionals}, overseeing the design and development of cutting-edge software products and spearheading digital transformation initiatives.
        \item Implemented Agile methodologies, resulting in a 20\% increase in project completion rate and reduced time-to-market by 15\%.
        \item Implemented SBL auto locate and PB Cross capability through Traiana integration, optimizing existing \textbf{\$20 billion CAD} of give-eligible swap balances, leading to \textbf{material cost savings of \$20 million} and over \textbf{860 hours saved annually} for the trading team.
        \item Revamped One Tick by re-platforming it on AWS cloud, resulting in an outstanding \textbf{70\% performance improvement}, along with \textbf{\$213,000} in hardware upgrade savings and a projected data savings of \textbf{\$707,800} over five years.
    \end{itemize}

    % Add other work experiences here...
    \item \textbf{Senior Software Engineer III | Bank Of America | Mumbai | Sep 2017 - Dec 2021} \\
    \textit{Equity Linked Technology, Investable Indices}
    \begin{itemize}[leftmargin=1em]
        \item Co-led a \textbf{globally distributed team of 13 software developers} to successfully build and maintain an investable indices platform comprising \textbf{400 indices}. The platform scaled to accommodate a \textbf{13-fold increase} in calculations (strategy, lifecycle, reconciliation, publication, reporting) and a \textbf{3-fold increase} in market data REST requests over a span of four years.
        \item Analyzed market data cost drivers and achieved significant savings of \textbf{\$350 million} through optimization using caching and alternative sourcing.
    \end{itemize}

    % Add other work experiences here...
    \item \textbf{Consultant | NRIFT | Mumbai | Jul 2015 - Aug 2017} \\
    \textit{Deutsche Bank, Financing Team}
    \begin{itemize}[leftmargin=1em]
        \item Led a team of 4 software developers to develop a Python-based reporting framework in an Agile environment. The framework separates content generation, report formatting, and report delivery into reusable configurations and supports email (using Jinja), PDF, Excel, CSV, and delivery channels like mail and SFTP. This initiative resulted in an impressive \textbf{90\% reduction} in client reporting FTE efforts.
    \end{itemize}

    % Add other work experiences here...
    \item \textbf{Consultant | Cognizant | Mumbai | Mar 2013 - Jul 2015} \\
    \textit{Credit Suisse, Global Market Risk Reporting}
    \begin{itemize}[leftmargin=1em]
        \item Achieved a \textbf{20\% reduction} in SLA breaches caused by technical incidents in APAC/EMEA regulatory risk report generation through workflow optimization and re-modeling. Spearheaded design discussions, confluence, agile meetings, data modeling, requirement analysis, and maintenance for Market Risk Systems, leading to increased stability and process resilience.
    \end{itemize}
\end{itemize}

% Technical Skills
\section*{\color{CarianBlue} \Large Technical Skills \crulefill{1pt}}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, Java, C++, SQL
    \item \textbf{Software Tools:} CICD (Git, GitHub Actions, JIRA, Jenkins, Docker), AWS (CLI, S3, Storage Gateway, EFS, Airflow, StepFunctions, Lambda), Messaging (MQ, AMPS, SQS, SNS)
    \item \textbf{Project Management:} Agile, Scrum, Kanban, Visio, Gliffy, TypeScript, Jira, Confluence
\end{itemize}

% Certifications
\section*{\color{CarianBlue} \Large Certifications \crulefill{1pt}}
\begin{itemize}
    \item \textbf{AWS Certified Solutions Architect – Associate | AWS | 2022-2025}
    \item \textbf{Certifications in Machine Learning, System Design, AWS, Terraform | Great Learning, Educative, Pluralsight, O’Reilly, Degreed | 2017 – Present}
    \item \textbf{Certified Financial Risk Manager (FRM) | Global Association Of Risk Professionals (GARP) | 2015 – 2016}
    \item \textbf{Certified National Capital Market Professional | National Stock Exchange of India (NSE) | 2011 – 2013}
    \item \textbf{Bachelor of Engineering in Computer Science | Dwarkadas J. Sanghvi College of Engineering | 2005 – 2009}
\end{itemize}

% Extracurricular & Additional Information
\section*{\color{CarianBlue} \Large Extracurricular \& Additional Information \crulefill{1pt}}
\begin{itemize}
    \item Led workshops on Building Trust and Psychological Safety - SCARF and SEEDS model effective collaboration within teams.
    \item Actively participated, won, and mentored in real-life code challenges and code-a-thons.
    \item Consistently received BOA's flagship platinum awards for project deliveries quarter on quarter.
    \item Passionate about teaching math, storytelling, and conducting yoga sessions for underprivileged school children through NGOs like Teach For India, United Ways, Agastya Foundation, Cognizant's Outreach, and Art of Living funded schools/programs.
    \item As Innovation SPOC, conducted patent grooming sessions and facilitated Python cohorts sessions, fostering a culture of innovation and learning.
\end{itemize}

\end{document}
